Tidal Locking in Low-Mass Stellar Binary Stars

### 2018-11-09 Paper/sync.tex

Plots:

-Porb vs Q/tau grid for e=0, and vs mass ratio

-average tsync for various orbital period ranges for CPL vs CTL marginalizing over all other parameters. do it with small multiples

-Prot as a function of mass for locked (unlocked) binaries of random ages for gyrochronology results, naturally produces fast rotators

-Plot showing diff between binary relative to single star Prot evolution for various Porbs

-tsync contours over Q/tau and Porb

@@

@@

\subsection{Tidal-Locking as a Function of Age} \label{sec:results:age}

@@

@@

@@

%\begin{figure}[h]
%	\includegraphics[width=0.45\textwidth]{../Plots/locked_kepler.pdf}
%   \caption{Simulated distribution of P$_{rot}$ for tidally-locked (cross) and unlocked (circle) stellar binaries, colored by age for Model 2 (see $\S$~\ref{sec:results:kepler2}). Left: P$_{rot}$ as a function of stellar mass.  Right: Marginalized P$_{rot}$ distribution for locked (blue) and unlocked (orange) binaries.  Tidally-locked binaries rotate more rapidly than unlocked binaries, displaying an increased density in the P$_{rot}$ distribution for P$_{rot} {\lsim} 20$ d, and with a median P$_{rot} = 19.8$ d, compared to the unlocked median P$_{rot} = 27.5$ d. Unlocked binaries on average rotate more quickly than single stars (compare to single distribution in Fig.~\ref{fig:kepler2}) due to the influence of tidal torques.}
%    \label{fig:locking}
%\end{figure}

>>>>

@@

\begin{figure*}[ht]
	\includegraphics[width=\textwidth]{../Plots/qTauPorbLockHist.pdf}
   \caption{Caption}%
    \label{fig:qTauLock}%
\end{figure*}

@@

\subsection{Tidal-Locking as a Function of Eccentricity} \label{sec:results:ecc}

\begin{figure*}[ht]
	\includegraphics[width=\textwidth]{../Plots/eccPorbLockHist.pdf}
   \caption{Caption.}%
    \label{fig:eccLock}%
\end{figure*}

\begin{figure*}[ht]
	\includegraphics[width=\textwidth]{../Plots/eccPorbRatioHist.pdf}
   \caption{Caption.}%
    \label{fig:eccRatio}%
\end{figure*}

@@

\subsection{Comparison with \kepler} \label{sec:kepler}

\begin{figure*}[ht]
	\includegraphics[width=\textwidth]{../Plots/lurie.pdf}
   \caption{Caption.}
    \label{fig:lurie}
\end{figure*}

@@

\begin{figure}[h]
	\includegraphics[width=0.45\textwidth]{../Plots/example.pdf}
   \caption{Caption}%
    \label{fig:binGyro}%
\end{figure}

@@

\begin{figure}[h]
	\includegraphics[width=0.45\textwidth]{../Plots/example.pdf}
   \caption{Caption}%
    \label{fig:lockingCPL}%
\end{figure}

\begin{figure}[h]
	\includegraphics[width=0.45\textwidth]{../Plots/example.pdf}
   \caption{Caption}%
    \label{fig:lockingCTL}%
\end{figure}
